---
title: "fars_vignette"
author: "Rick"
date: "2023-01-23"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(Week4)
```

The purpose of this assessment is for you to combine your skills of creating, writing, documenting, and testing an R package with releasing that package on GitHub. In this assessment you'll be taking the R files from Week 2's assessment about documentation and putting that file in an R package. 

For this assessment you must

 - write a vignette to include in your package using knitr and R Markdown
 - write at least one test written using testthat
 - put your package on GitHub
 - set up the repository so that the package can be checked and built on Travis
 - Once your package has built on Travis and the build is passing with no errors, warnings, or -  - notes you should add your Travis badge to the README.md file of your package repository.

## 1. Write vignette
`use_vignette("fars_vignette")`.

## 2. Write one test
`./test/testthat.r`.

## 3. Put package on GitHub
uploaded

## 4. Set up Travis
`use_travis()` or `use_github_actions()`


